R Markdown for Reproducible Research

### 2019-01-07 paper.Rmd
tweak whitespace presentation

We will focus on R code for now, and come back to the other languages later. R
Markdown has a handful of noteworthy differences from general Markdown. First,
every R Markdown document begins with a YAML header:

@@

The most noteworthy difference about R Notebooks versus plain R Markdown is that
they are somewhat _stateful_. This means that they cache and display output as
it is generated, making it easier to interactively and iteratively build a
narrative without having to re-render the document each time you have made a
change.

@@

As a result, R Notebooks can be thought about as good for interactive
exploration or discussion among developers, but moving to an R Markdown format
is generally preferred once the report has stabilized or is being shared with an
end user.

@@

## WHAT ABOUT THE OTHER LANGUAGES?

@@

>>>>

R Markdown has a handful of noteworthy differences from general Markdown. First,
every R Markdown document begins with a YAML header:

@@

There can be [many reasons](todo) that a user might prefer R Notebooks, but the
most noteworthy difference between R Notebooks and plain R Markdown is that R
Notebooks are somewhat _stateful_. This means that they cache and display output
as it is generated, making it easier to interactively and iteratively build a
narrative without having to re-render the document each time you have made a
change.

@@

As a result, R Notebooks can be thought about as good for interactive
exploration or discussion among developers, but moving to a standard R Markdown
format is generally preferred once the report has stabilized or is being shared
with an end user.

@@

@@

A little known feature of R Markdown is the ability to add _parameters_.
Parameterized R Markdown is defined by adding parameters to the YAML header,
which will then be utilized within the rendering of the document.
